Incidence of confirmed COVID-19 cases in care home staff and residents: Cohort study using electronic records in a large UK care home provider (March-June 2020)

### 2020-06-25 covidWarehouse/manuscript/manuscript.Rmd
manuscript version 0.2

```{r descriptives}

@@

residents_overview <- tline %>% 
  filter(rday==1) %>%
  mutate(ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95)) %>% 
  group_by(resident_id, home_code, ageg, gender, 
           admission_type2, home_type, user_type2, status) %>% 
  summarise(resident_days = sum(rday),
            susceptible_symptomatic_days = sum(susceptible_symptomatic),
            susceptible_confirmed_days = sum(susceptible_confirmed),
            symptomatic = max(-susceptible_symptomatic+1, na.rm = T),
            confirmed = max(-susceptible_confirmed+1, na.rm = T),
            start_date = min(date, na.rm = T),
            stop_date = max(date, na.rm = T),
            start_int = as.numeric(min(date, na.rm = T) - date_min),
            stop_int = as.numeric(max(date, na.rm = T)- date_min)
    ) %>% 
  mutate(covid_status = case_when(
    symptomatic==0 & confirmed == 0 ~ "Negative",
    symptomatic==1 & confirmed == 0 ~ "Symptomatic (not confirmed)",
    symptomatic==0 & confirmed == 1 ~ "Asymptomatic confirmed",
    symptomatic==1 & confirmed == 1 ~ "Symptomatic confirmed"
  )) %>% 
  mutate(covid_status = factor(covid_status, 
                               levels = c("Negative", "Symptomatic (not confirmed)",
                                          "Asymptomatic confirmed", "Symptomatic confirmed"))) %>% 
  left_join(select(reference_homes, home_code, country, region_UK,
                   staff_to_bed_ratio, carer_to_bed_ratio, bed_tot_category)) %>% 
  left_join(distinct(select(incidents, resident_id, starts_with("covid_first"))))

@@

desc_overall <- list()
desc_overall$total_residents <- dplyr::n_distinct(residents_overview$resident_id)
desc_overall$total_staff <- reference_homes %>% filter(home_code %in% unique(residents_overview$home_code)) %>% .$staff_total %>% sum()

#COUNTS
desc_overall$CT_total_symptomatic <- sum(new_cases$new_symptomatic_home, na.rm=T) + 
  sum(new_cases$new_symptomatic_hospital, na.rm=T)
desc_overall$CT_p_symptomatic <- desc_overall$CT_total_symptomatic/desc_overall$total_residents
desc_overall$CT_p_symptomatic_ME <- 1.96 * sqrt(
  (desc_overall$CT_p_symptomatic*(1-desc_overall$CT_p_symptomatic)/desc_overall$total_residents)
)
desc_overall$CT_total_confirmed <-  sum(new_cases$new_confirmed_home, na.rm = T) +
  sum(new_cases$new_confirmed_hospital, na.rm = T)
desc_overall$CT_p_confirmed <- desc_overall$CT_total_confirmed/desc_overall$total_residents
desc_overall$CT_p_confirmed_ME <- 1.96 * sqrt(
  desc_overall$CT_p_confirmed * (1-desc_overall$CT_p_confirmed) / 
    desc_overall$total_residents
)
#INCIDENT REPORTS
desc_overall$unique_residents_incidents <- dplyr::n_distinct(incidents$resident_id)

desc_overall$DAT_total_symptomatic <- n_distinct(filter(incidents, !is.na(covid_first_symptomatic))$resident_id)
desc_overall$DAT_p_symptomatic <- desc_overall$DAT_total_symptomatic/desc_overall$total_residents
desc_overall$DAT_p_symptomatic_ME <- 1.96 * sqrt(
  desc_overall$DAT_p_symptomatic * (1 - desc_overall$DAT_p_symptomatic) / 
    desc_overall$total_residents
)

desc_overall$total_tests <- nrow(dplyr::filter(incidents, covid_tested == 1))
desc_overall$unique_residents_tested <- dplyr::filter(incidents, covid_tested == 1) %>% 
  dplyr::summarise(n = n_distinct(resident_id)) %>% .$n
desc_overall$unique_residents_test_result <- dplyr::filter(incidents, !is.na(covid_test_result)) %>% 
  dplyr::summarise(n = n_distinct(resident_id)) %>% .$n
desc_overall$unique_residents_test_result_positive <- dplyr::filter(incidents, covid_test_result == 1) %>%  
  dplyr::summarise(n = n_distinct(resident_id)) %>% .$n

desc_overall$DAT_p_confirmed <- desc_overall$unique_residents_test_result_positive/desc_overall$total_residents
desc_overall$DAT_p_confirmed_ME <- 1.96 * sqrt(
  desc_overall$DAT_p_confirmed * (1-desc_overall$DAT_p_confirmed) / 
    desc_overall$total_residents
)

desc_overall$DAT_incidence_confirmed <- desc_overall$unique_residents_test_result_positive/sum(residents_overview$susceptible_confirmed_days)
desc_overall$DAT_incidence_confirmed_SE <- sqrt((1-desc_overall$DAT_incidence_confirmed)/desc_overall$unique_residents_test_result_positive)
desc_overall$DAT_incidence_confirmed_95low <- exp(
  log(desc_overall$DAT_incidence_confirmed - 1.96 * desc_overall$DAT_incidence_confirmed_SE)
)
desc_overall$DAT_incidence_confirmed_95up <- exp(
  log(desc_overall$DAT_incidence_confirmed + 1.96 * desc_overall$DAT_incidence_confirmed_SE)
)

home_total_confirmed_DAT <- filter(incidents, !is.na(covid_first_symptomatic)) %>% 
  group_by(home_code) %>% 
  summarise(DAT_confirmed = tidyr::replace_na(n_distinct(resident_id), 0))
home_total_confirmed_CT <- new_cases %>% group_by(home_code) %>% 
  summarise(CT_confirmed = sum(tidyr::replace_na(new_confirmed_home, 0) + 
                                 tidyr::replace_na(new_confirmed_hospital, 0)))

@@

desc_overall$total_homes <- n_distinct(home_total_confirmed$home_code)
desc_overall$CT_zero_case <- sum(home_total_confirmed$CT_confirmed == 0)
desc_overall$DAT_zero_case <- sum(home_total_confirmed$DAT_confirmed == 0)

@@

## TABLES
table_nums <- captioner::captioner(prefix = "Table")
tab_national_descriptives <- table_nums(
  name = "tab_national_descriptives",
  caption = "Total homes, beds, and residents within FSHCG and nationwide")
tab_resident_descriptives <- table_nums(
  name = "tab_resident_descriptives",
  caption = paste0("Breakdown of FSHCG residents by care home type, sex, age, region and status on study exit (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
tab_zero_cases <- table_nums(
  name = "tab_zero_cases",
  caption = "Number and proportion of homes without confirmed cases by UK region"
)
tab_CoxPH_confirmed <- table_nums(
  name = "tab_CoxPH_confirmed",
  caption =  paste0("Factors associated with the hazard of become a confirmed case: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))
tab_CoxPH_death <- table_nums(
  name = "tab_CoxPH_death",
  caption =  paste0("Factors associated with all-cause mortality: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))
## FIGURES
fig_nums <- captioner(prefix = "Figure")

fig_KM_CT_residents_symptomatic <- fig_nums(
  name = "fig_KM_CT_residents_symptomatic",
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of residents becoming symptomatic based on care home manager daily counts")
)
fig_KM_residents_confirmed <- fig_nums(
  name = 'fig_KM_residents_confirmed',
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of residents (n=",
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ") becoming confirmed cases based on Datix incidents report"))
fig_KM_CT_confirmed_residents <- fig_nums(
  name = 'fig_KM_CT_confirmed_residents',
  caption = "Kaplan-Meier estimates of the cumulative probability of residents becoming confirmed cases based on care home manager daily counts")
fig_KM_mortality <- fig_nums(
  "fig_KM_mortality",
  caption = paste0("Kaplan-Meier estimates of resident (n=",
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ") survival by SARS-COV-2 case type"))
fig_KM_staff_symptomatic <- fig_nums(
  name = 'fig_KM_staff_symptomatic',
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of care home staff (n=",   formatbm(desc_overall$total_staff),
  ") becoming symptomatic cases based on manager-reported daily counts"))
fig_KM_staff_confirmed <- fig_nums(
  name = 'fig_KM_staff_confirmed',
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of care home staff (n=",   formatbm(desc_overall$total_staff),
  ") becoming confirmed cases based on manager-reported daily counts"))

@@

RR_england <- relative_risk(
  a = england_results$n_positive,
  b = england_results$n_negative,
  c = cis_data$n_positive,
  d = cis_data$n_negative)

RR_SE <- relative_risk_SE(
  a = england_results$n_positive,
  b = england_results$n_negative,
  c = cis_data$n_positive,
  d = cis_data$n_negative)
```

@@

**Findings:** Records were available for `r formatbm(n_distinct(residents_overview$resident_id))` residents present in `r dplyr::n_distinct(residents$home_code)` FSHCG homes between `r format(date_min, "%e %B %Y")` and `r format(date_max, "%e %B %Y")`. The incidence proportion of COVID-19 symptoms ranged between `r tbrounding(desc_overall$DAT_p_symptomatic*100)`% (based on incidents reports) and `r tbrounding(desc_overall$CT_p_symptomatic*100)`% (based on manager-reported counts). Across the period, care homes registered a total of `r formatbm(desc_overall$CT_total_confirmed)` (`r tbrounding(desc_overall$CT_p_confirmed*100)`% [`r tbrounding((desc_overall$CT_p_confirmed - desc_overall$CT_p_confirmed_ME)*100)`%; `r tbrounding((desc_overall$CT_p_confirmed + desc_overall$CT_p_confirmed_ME)*100)`%]) infections confirmed with nasopharyngeal RNA tests. Incident reports accounted just `r formatbm(desc_overall$unique_residents_test_result_positive)` confirmed infections. In England, `r england_results$n_positive` infections were confirmed of a total `r formatbm(england_results$n_positive + england_results$n_negative)` residents. Comparing with the community, the relative risk of confirmed cases in England was `r tbrounding(RR_england)` [`r tbrounding(exp(log(RR_england) - 1.96 * RR_SE)) `; `r tbrounding(exp(log(RR_england) + 1.96 * RR_SE))`]. The staff-to-bed ratio was the only factor to be independently associated with the rate of confirmed cases: an increase by 10 percentage point in the number of staff relative to the bed total was associated with a 13% reduction [9%, 18%] in the rate of confirmed cases.

@@

An important source of epidemiological data on the burden of disease in care homes are outbreak investigations.[@McMichael2020; @Dora2020] One such investigation estimated that 50% of residents and 20% of staff are infected during an outbreak in London, UK.[@Easter6] Estimates of this nature cannot be generalised to the unknown proportion of care homes that have not reported any outbreaks.

@@

We obtained care home organisational characteristics: staff headcounts, bed counts, ***latest Care Quality Commission rating***, and types of care available (nursing dementia; nursing general; residential dementia; residential general; younger person).

@@

Data were analysed in `R`3·5·0[@RCoreTeam2018] and the `survival` package.[@therneau2015] All computer syntax is available on an online repository.[@Dutey2020]

@@

The study population consisted of `r formatbm(desc_overall$total_residents)` residents across England, Scotland and Northern Ireland, `r tbrounding(mean(residents$home_type=="Nursing")*100)`% of whom were in nursing homes and 39·2% received dementia care (`r table_nums("tab_resident_descriptives", display = "cite")`). The vast majority (85·4%) were permanent residents. A total of `r formatbm(nrow(incidents))` COVID-19 incidents were reported on Datix as of `r format(max(incidents$incident_date), "%A %e %b %Y")` for  `r formatbm(desc_overall$unique_residents_incidents)` unique residents. The reports were returned by `r formatbm(dplyr::n_distinct(incidents$home_code))` care homes  totalling `r formatbm(sum(beds[beds$year=="2020" & beds$home_code %in% unique(incidents$home_code), "beds"]))` beds.

Datix reports and manager counts respectively indicated that `r formatbm(desc_overall$DAT_total_symptomatic)` (`r tbrounding(desc_overall$DAT_p_symptomatic*100)`% [95% confidence interval: `r tbrounding((desc_overall$DAT_p_symptomatic - desc_overall$DAT_p_symptomatic_ME)*100)`; `r tbrounding((desc_overall$DAT_p_symptomatic + desc_overall$DAT_p_symptomatic_ME)*100)`]) and `r formatbm(desc_overall$CT_total_symptomatic)` (`r tbrounding(desc_overall$CT_p_symptomatic*100)`% [`r tbrounding((desc_overall$CT_p_symptomatic - desc_overall$CT_p_symptomatic_ME)*100)`; `r tbrounding((desc_overall$CT_p_symptomatic + desc_overall$CT_p_symptomatic_ME)*100)`]) residents became symptomatic at some point between `r format(date_min, "%e %B %Y")` and `r format(date_max, "%e %B %Y")`. Temporal trends broken down by region (`r fig_nums("fig_KM_CT_residents_symptomatic", display = "cite")`) indicate wide variation across the UK, with care homes in the South East and Northern Ireland reporting in excess of a third of residents with symptoms.

@@

```{r table_resident_descriptives, message = FALSE, results="asis"}
arsenal::tableby(home_type  ~ gender + ageg + region_UK +
   user_type2 + admission_type2 + covid_status + status +
   resident_days + susceptible_symptomatic_days + susceptible_confirmed_days, 
   control = arsenal::tableby.control(test = FALSE, numeric.stats = c("Nmiss", "meansd"), digits = 1L),
   data = residents_overview) %>% summary()
```

```{r KM_CT_residents_symptomatic, fig.height = 4, fig.width = 8}

order_key <-km_ct_residents_symp %>% 
  group_by(region_UK) %>% 
  summarise(S_t = min(S_t)) %>% 
  arrange(S_t)
km_ct_residents_symp$region_UK <- factor(
  km_ct_residents_symp$region_UK,
  levels = order_key$region_UK
)
km_ct_residents_symp$region_group <- cut(as.integer(km_ct_residents_symp$region_UK), 2, labels = 1:2)

@@

```{r KM_CT_residents_infection, fig.height = 4, fig.width = 8}

>>>>

```{r init_data}

@@

residents_overview <- tline %>% 
  filter(rday==1) %>%
  mutate(ageg = cut_age_denary(compute_age(dob, date_min), age.min = 75, age.max = 95)) %>% 
  group_by(resident_id, home_code, ageg, gender, 
           admission_type2, home_type, user_type2, status) %>% 
  summarise(resident_days = sum(rday),
            susceptible_symptomatic_days = sum(susceptible_symptomatic),
            susceptible_confirmed_days = sum(susceptible_confirmed),
            symptomatic = max(-susceptible_symptomatic+1, na.rm = T),
            confirmed = max(-susceptible_confirmed+1, na.rm = T),
            start_date = min(date, na.rm = T),
            stop_date = max(date, na.rm = T),
            start_int = as.numeric(min(date, na.rm = T) - date_min),
            stop_int = as.numeric(max(date, na.rm = T)- date_min)
    ) %>% 
  ungroup() %>% 
  mutate(covid_status = case_when(
    symptomatic==0 & confirmed == 0 ~ "Negative",
    symptomatic==1 & confirmed == 0 ~ "Symptomatic (not confirmed)",
    symptomatic==0 & confirmed == 1 ~ "Asymptomatic confirmed",
    symptomatic==1 & confirmed == 1 ~ "Symptomatic confirmed"
  )) %>% 
  mutate(covid_status = factor(covid_status, 
                               levels = c("Negative", "Symptomatic (not confirmed)",
                                          "Asymptomatic confirmed", "Symptomatic confirmed"))) %>% 
  left_join(select(reference_homes, home_code, country, region_UK,
                   staff_to_bed_ratio, carer_to_bed_ratio, bed_tot_category)) %>% 
  left_join(distinct(select(incidents, resident_id, starts_with("covid_first"))))

# CARE HOME AGGREGATES
home_total_confirmed_DAT <- filter(incidents, !is.na(covid_first_symptomatic)) %>% 
  group_by(home_code) %>% 
  summarise(DAT_confirmed = tidyr::replace_na(n_distinct(resident_id), 0))
home_total_confirmed_CT <- new_cases %>% group_by(home_code) %>% 
  summarise(CT_confirmed = sum(tidyr::replace_na(new_confirmed_home, 0) + 
                                 tidyr::replace_na(new_confirmed_hospital, 0)))

@@

@@

@@

```{r km_objects}

km_staff_confirmed <- staff_ct %>% 
  group_by(date, region_UK) %>% 
  summarise(
    confirmed = sum(tidyr::replace_na(new_colleague_confirmed, 0)),
    symptomatic = sum(tidyr::replace_na(new_colleague_symptomatic, 0)),
    staff_total = sum(staff_total)
  ) %>% 
  group_by(region_UK) %>% 
  km_ct_estimator(., date, confirmed, staff_total) %>% 
  ungroup() %>% 
  mutate(
    St_max = S_t^exp(1.96*S_t_SElog),
    St_min = S_t^exp(-1.96*S_t_SElog)
  )

desc_staff <- list()
desc_staff$total_staff <- reference_homes %>% filter(home_code %in% unique(residents_overview$home_code)) %>% .$staff_total %>% sum()

desc_staff$CT_symptomatic_total <- sum(new_cases$new_colleague_symptomatic, na.rm = T)
desc_staff$CT_symptomatic_denom <- sum(km_staff_symptomatic$n_t)

desc_staff[paste0(
  "CT_symptomatic_p", c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_staff$CT_symptomatic_total,
  desc_staff$total_staff)[c("proportion", "lower", "upper")] *100

desc_staff[paste0(
  "CT_symptomatic_IR", c("", "_lower", "_upper")
)] <- epitools::pois.exact(
  desc_staff$CT_symptomatic_total,
  desc_staff$CT_symptomatic_denom)[c("rate", "lower", "upper")] *100000

desc_staff$CT_confirmed_total <- sum(new_cases$new_colleague_confirmed, na.rm = T)
desc_staff$CT_confirmed_denom <- sum(km_staff_confirmed$n_t)
desc_staff[paste0(
  "CT_confirmed_p", c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_staff$CT_confirmed_total,
  desc_staff$total_staff)[c("proportion", "lower", "upper")] *100

desc_staff[paste0(
  "CT_confirmed_IR", c("", "_lower", "_upper")
)] <- epitools::pois.exact(
  desc_staff$CT_confirmed_total,
  desc_staff$CT_confirmed_denom)[c("rate", "lower", "upper")] *100000

```{r descriptives}
desc_residents <- list()
desc_residents$total_residents <- dplyr::n_distinct(residents_overview$resident_id)

#COUNTS
desc_residents$CT_total_symptomatic <- sum(new_cases$new_symptomatic_home, na.rm=T) + 
  sum(new_cases$new_symptomatic_hospital, na.rm=T)
desc_residents$CT_total_symptomatic_denom <- sum(km_ct_residents_symp$n_t)
desc_residents[paste0(
  "CT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$CT_total_symptomatic,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

desc_residents[paste0(
  "CT_IR_symptomatic", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents$CT_total_symptomatic,
                            desc_residents$CT_total_symptomatic_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

desc_residents$CT_total_confirmed <-  sum(new_cases$new_confirmed_home, na.rm = T) + sum(new_cases$new_confirmed_hospital, na.rm = T)
desc_residents$CT_total_confirmed_denom <- sum(km_ct_residents_confirmed$n_t)

desc_residents[paste0(
  "CT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$CT_total_confirmed,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

desc_residents[paste0(
  "CT_IR_confirmed", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents$CT_total_confirmed,
                            desc_residents$CT_total_confirmed_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

#INCIDENT REPORTS
desc_residents$unique_residents_incidents <- dplyr::n_distinct(incidents$resident_id)

desc_residents$DAT_total_symptomatic <- n_distinct(filter(incidents, !is.na(covid_first_symptomatic))$resident_id)
desc_residents$DAT_total_symptomatic_denom <- sum(residents_overview$susceptible_symptomatic_days)
desc_residents[paste0(
  "DAT_p_symptomatic", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$DAT_total_symptomatic,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100
desc_residents[paste0(
  "DAT_IR_symptomatic", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents$DAT_total_symptomatic,
                            desc_residents$DAT_total_symptomatic_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

desc_residents$total_tests <- nrow(dplyr::filter(incidents, covid_tested == 1))
desc_residents$unique_residents_tested <- dplyr::filter(incidents, covid_tested == 1) %>% 
  dplyr::summarise(n = n_distinct(resident_id)) %>% .$n
desc_residents$unique_residents_test_result <- dplyr::filter(incidents, !is.na(covid_test_result)) %>% 
  dplyr::summarise(n = n_distinct(resident_id)) %>% .$n
desc_residents$unique_residents_test_result_positive <- dplyr::filter(incidents, covid_test_result == 1) %>%  
  dplyr::summarise(n = n_distinct(resident_id)) %>% .$n

desc_residents$DAT_total_confirmed_denom <- sum(residents_overview$susceptible_confirmed_days)
desc_residents[paste0(
  "DAT_p_confirmed", c("", "_lower", "_upper")
)] <- epitools::binom.exact(desc_residents$unique_residents_test_result_positive,
                            desc_residents$total_residents)[
                              c("proportion", "lower", "upper")
                            ] * 100

desc_residents[paste0(
  "DAT_IR_confirmed", c("", "_lower", "_upper")
)] <- epitools::pois.exact(desc_residents$unique_residents_test_result_positive,
                            desc_residents$DAT_total_confirmed_denom)[
                              c("rate", "lower", "upper")
                            ] * 100000

# CASE FATALITY AND RELATIVE RISK

desc_residents$DAT_total_deaths <- sum(residents_overview$status == "Deceased")
desc_residents$total_denom <- sum(residents_overview$resident_days)
desc_residents[paste0(
  "DAT_p_death",  c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_residents$DAT_total_deaths,
  desc_residents$total_residents
)[c("proportion", "lower", "upper")] *100

desc_residents[paste0(
  "DAT_IR_death",  c("", "_lower", "_upper")
)] <- epitools::pois.exact(
  desc_residents$DAT_total_deaths,
  desc_residents$total_denom
)[c("rate", "lower", "upper")] * 100000

desc_residents$DAT_CFR <- residents_overview %>% 
  filter(confirmed == 1) %>% 
  summarise(n = n(),
            y = sum(status == "Deceased"))

desc_residents$DAT_BFR <- residents_overview %>%
  filter(confirmed != 1) %>%
  summarise(n = n(),
            y = sum(status == "Deceased"))

desc_residents$DAT_CFR_RR <- relative_risk(desc_residents$DAT_CFR$y, desc_residents$DAT_CFR$n - desc_residents$DAT_CFR$y, desc_residents$DAT_BFR$y, desc_residents$DAT_BFR$n - desc_residents$DAT_BFR$y)

desc_residents$DAT_CFR_RR_SE <- relative_risk_SE(desc_residents$DAT_CFR$y, desc_residents$DAT_CFR$n - desc_residents$DAT_CFR$y, desc_residents$DAT_BFR$y, desc_residents$DAT_BFR$n - desc_residents$DAT_BFR$y)

desc_residents[paste0(
  "DAT_CFR", c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_residents$DAT_CFR$y,
  desc_residents$DAT_CFR$n
)[c("proportion", "lower", "upper")] *100

desc_residents[paste0(
  "DAT_BFR", c("", "_lower", "_upper")
)] <- epitools::binom.exact(
  desc_residents$DAT_BFR$y,
  desc_residents$DAT_BFR$n
)[c("proportion", "lower", "upper")] *100

### Homes
desc_residents$total_homes <- n_distinct(home_total_confirmed$home_code)
desc_residents$CT_zero_case <- sum(home_total_confirmed$CT_confirmed == 0)
desc_residents$DAT_zero_case <- sum(home_total_confirmed$DAT_confirmed == 0)
```

```{r captions}
## TABLES
table_nums <- captioner::captioner(prefix = "Table")
tab_national_descriptives <- table_nums(
  name = "tab_national_descriptives",
  caption = "Total homes, beds, and residents within FSHCG and nationwide")
tab_resident_descriptives <- table_nums(
  name = "tab_resident_descriptives",
  caption = paste0("Breakdown of FSHCG residents by care home type, sex, age, region and status on study exit (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
tab_zero_cases <- table_nums(
  name = "tab_zero_cases",
  caption = "Number and proportion of homes without confirmed cases by UK region"
)
tab_CoxPH_confirmed <- table_nums(
  name = "tab_CoxPH_confirmed",
  caption =  paste0("Factors associated with the hazard of become a confirmed case: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))
tab_CoxPH_death <- table_nums(
  name = "tab_CoxPH_death",
  caption =  paste0("Factors associated with all-cause mortality: hazard ratios (HR) from a Cox proportional hazards model (n=", 
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ")"))

supp_epi_CT <- table_nums(
  name = "supp_epi_CT",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections in residents and staff according to FSHCG manager counts (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))
supp_epi_DAT <- table_nums(
  name = "supp_epi_DAT",
  caption =  paste0("Incidence proportions and rates of SARS-CoV-2 infections amongst residents according to Datix incident reports (", format(date_min, "%d/%m/%y"), "-", format(date_max, "%d/%m/%y"), ")"))

## FIGURES
fig_nums <- captioner(prefix = "Figure")

fig_KM_CT_residents_symptomatic <- fig_nums(
  name = "fig_KM_CT_residents_symptomatic",
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of residents becoming symptomatic based on care home manager daily counts")
)
fig_KM_residents_confirmed <- fig_nums(
  name = 'fig_KM_residents_confirmed',
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of residents (n=",
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ") becoming confirmed cases based on Datix incidents report"))
fig_KM_CT_confirmed_residents <- fig_nums(
  name = 'fig_KM_CT_confirmed_residents',
  caption = "Kaplan-Meier estimates of the cumulative probability of residents becoming confirmed cases based on care home manager daily counts")
fig_KM_mortality <- fig_nums(
  "fig_KM_mortality",
  caption = paste0("Kaplan-Meier estimates of resident (n=",
  formatbm(dplyr::n_distinct(residents_overview$resident_id)),
  ") survival by SARS-COV-2 case type"))
fig_KM_staff_symptomatic <- fig_nums(
  name = 'fig_KM_staff_symptomatic',
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of care home staff (n=",   formatbm(desc_staff$total_staff),
  ") becoming symptomatic cases based on manager-reported daily counts"))
fig_KM_staff_confirmed <- fig_nums(
  name = 'fig_KM_staff_confirmed',
  caption = paste0("Kaplan-Meier estimates of the cumulative probability of care home staff (n=",   formatbm(desc_staff$total_staff),
  ") becoming confirmed cases based on manager-reported daily counts"))

@@

england_results$RR_england <- relative_risk(
  a = england_results$n_positive,
  b = england_results$n_negative,
  c = cis_data$n_positive,
  d = cis_data$n_negative)

england_results$RR_SE <- relative_risk_SE(
  a = england_results$n_positive,
  b = england_results$n_negative,
  c = cis_data$n_positive,
  d = cis_data$n_negative)
```

@@

**Findings:** Records were available for `r formatbm(n_distinct(residents_overview$resident_id))` residents present in `r dplyr::n_distinct(residents$home_code)` FSHCG homes between `r format(date_min, "%e %B %Y")` and `r format(date_max, "%e %B %Y")`. During this period `r formatbm(desc_residents$CT_total_symptomatic_denom)` residents developed COVID-19 symptoms (`r tbrounding(desc_residents$CT_p_symptomatic)`% [95% confidence interval: `r tbrounding(desc_residents$CT_p_symptomatic_lower)`%; `r tbrounding(desc_residents$CT_p_symptomatic_upper)`%]), and `r formatbm(desc_residents$CT_total_confirmed)` (`r tbrounding(desc_residents$CT_p_confirmed)`% [`r tbrounding(desc_residents$CT_p_confirmed_lower)`%; `r tbrounding(desc_residents$CT_p_confirmed_upper)`%]) had an infection confirmed with nasopharyngeal RNA tests. Across all care homes, the confirmed infection rate of incidence was `r tbrounding(desc_residents$CT_IR_confirmed)` per 100,000 resident-days [`r tbrounding(desc_residents$CT_IR_confirmed_lower)`; `r tbrounding(desc_residents$CT_IR_confirmed_upper)`]. In England, `r england_results$n_positive` infections were confirmed of a total `r formatbm(england_results$n_positive + england_results$n_negative)` residents. Comparing with the community, the relative risk of confirmed cases in England was `r tbrounding(england_results$RR_england)` [`r tbrounding(exp(log(england_results$RR_england) - 1.96 * england_results$RR_SE)) `; `r tbrounding(exp(log(england_results$RR_england) + 1.96 * england_results$RR_SE))`]. The staff-to-bed ratio was the only factor to be independently associated with the rate of confirmed cases: an increase by 10 percentage point in the number of staff relative to the bed total was associated with a 13% reduction [9%, 18%] in the rate of confirmed cases. Out of `r formatbm(desc_staff$total_staff)` staff, `r formatbm(desc_staff$CT_confirmed_total)` confirmed infections were counted(
`r tbrounding(desc_staff$CT_confirmed_p)`% [`r tbrounding(desc_staff$CT_confirmed_p_lower)`%; `r tbrounding(desc_staff$CT_confirmed_p_upper)`%]), corresponding to a rate of incidence of 
`r tbrounding(desc_staff$CT_confirmed_IR)` per 100,000 staff-days [`r tbrounding(desc_staff$CT_symptomatic_IR_lower)`; `r tbrounding(desc_staff$CT_symptomatic_IR_upper)`].

@@

An important source of epidemiological data on the burden of disease in care homes are outbreak investigations.[@McMichael2020; @Dora2020] A living systematic review[@Salcher-Konrad2020] of outbreak investigations found incidence proportions ranging between 0% and 72% among residents and between 2% and 64% among staff of long term care facilities. Estimates of this nature cannot be generalised due to the unknown proportion of care homes that have not reported any outbreaks.

@@

We obtained care home organisational characteristics: staff headcounts, bed counts, and types of care available (nursing dementia; nursing general; residential dementia; residential general; younger person).

@@

Data were analysed in `R`3·5·0[@RCoreTeam2018] using the `epitool`[@Aragon2020] and `survival`[@therneau2015] libraries. All computer syntax is available on an online repository.[@Dutey2020] Ninety-five percent confidence intervals for proportions and rates were computed from the exact Poisson and binomial limits.

@@

The study population consisted of `r formatbm(desc_residents$total_residents)` residents across England, Scotland and Northern Ireland, `r tbrounding(mean(residents$home_type=="Nursing")*100)`% of whom were in nursing homes and 39·2% received dementia care (`r table_nums("tab_resident_descriptives", display = "cite")`). The vast majority (85·4%) were permanent residents. A total of `r formatbm(nrow(incidents))` COVID-19 incidents were reported on Datix as of `r format(max(incidents$incident_date), "%A %e %b %Y")` for  `r formatbm(desc_residents$unique_residents_incidents)` unique residents. The reports were returned by `r formatbm(dplyr::n_distinct(incidents$home_code))` care homes  totalling `r formatbm(sum(beds[beds$year=="2020" & beds$home_code %in% unique(incidents$home_code), "beds"]))` beds.

Datix reports and manager counts respectively indicated that `r formatbm(desc_residents$DAT_total_symptomatic)` (`r tbrounding(desc_residents$DAT_p_symptomatic)`% [95% confidence interval: `r tbrounding(desc_residents$DAT_p_symptomatic_lower)`%; `r tbrounding(desc_residents$DAT_p_symptomatic_upper)`%]) and `r formatbm(desc_residents$CT_total_symptomatic)` (`r tbrounding(desc_residents$CT_p_symptomatic)`% [`r tbrounding(desc_residents$CT_p_symptomatic_lower)`%; `r tbrounding(desc_residents$CT_p_symptomatic_upper)`%]) residents became symptomatic at some point between `r format(date_min, "%e %B %Y")` and `r format(date_max, "%e %B %Y")` (`table_nums("supp_epi_CT", display = "cite")`). Temporal trends broken down by region (`r fig_nums("fig_KM_CT_residents_symptomatic", display = "cite")`) indicate wide variation across the UK, with care homes in the South East and Northern Ireland reporting in excess of a third of residents with symptoms.

@@

```{r table_resident_descriptives, message = FALSE, results="asis"}
arsenal::tableby(home_type  ~ gender + ageg  +
   user_type2 + admission_type2 + covid_status + status + region_UK, 
   control = arsenal::tableby.control(test = FALSE, numeric.stats = c("Nmiss", "meansd"), digits = 1L),
   data = residents_overview) %>% summary()
```

```{r KM_CT_residents_symptomatic, fig.height = 4, fig.width = 8}
order_key <-km_ct_residents_symp %>% 
  group_by(region_UK) %>% 
  summarise(S_t = min(S_t)) %>% 
  arrange(S_t)
km_ct_residents_symp$region_UK <- factor(
  km_ct_residents_symp$region_UK,
  levels = order_key$region_UK
)
km_ct_residents_symp$region_group <- cut(as.integer(km_ct_residents_symp$region_UK), 2, labels = 1:2)

@@

```{r KM_CT_residents_infection, fig.height = 4, fig.width = 8}
order_key <-km_ct_residents_confirmed %>% 
  group_by(region_UK) %>% 
  summarise(S_t = min(S_t)) %>% 
  arrange(S_t)
km_ct_residents_confirmed$region_UK <- factor(
  km_ct_residents_confirmed$region_UK,
  levels = order_key$region_UK
)
km_ct_residents_confirmed$region_group <- cut(as.integer(km_ct_residents_confirmed$region_UK), 2, labels = 1:2)
